Staged Abstract Interpreters

### 2019-04-06 paper/10_intro.tex
typo

\paragraph{Contributions} Briefly, the contribution of the paper is twofold:
\begin{enumerate}[leftmargin=2em]
  \item Intellectually, through multi-stage programming, we present a unified construction 
    that naturally extends the first Futamura projection to abstract interpreters.
 \item Pragmatically, by case studies and empirical evaluation, we show that staging 
   abstract interpreters is useful to improve performance while \note{not a word} untouch 
   the soundness. 
\end{enumerate}
\paragraph{Organization} The paper is organized as follows:
\begin{itemize}[leftmargin=2em]
\item Starting from a generic interface of the interpreter for a small higher-order language
  (Section~\ref{prelim}), we first show the instantiation of concrete
  interpretation (Section~\ref{unstaged_conc}), and then lift it to the staged
  version by replacing the binding-time types (Section~\ref{stagedinterp}).
\item We discuss the unstaged abstract interpreter under the same framework by
  replacing the environment, store and values (Section~\ref{unstaged_abs}).
  Finally, we show the combination of approximation and specialization, dubbed
  \textit{staged abstract interpreters}, can be readily derived (Section~\ref{sai}).
\item We conduct three case studies on the applicability of our approach
  (Section~\ref{cases_study}).
  \begin{enumerate}
  \item We first revisit the Abstract Compilation (AC)
    \cite{Boucher:1996:ACN:647473.727587} (Section~\ref{cs_ac}), showing that we can
    achieve the same optimization with much less engineering effort.
  \item We extend the staged abstract interpreter to various control-flow
    analysis (Section \ref{cfa}), including context-sensitivity, store-widening, and abstract
    garbage collection, showing that our approach is widely applicable.
  \item We apply our approach to modular analysis (Section \ref{modular}),
    i.e., analyzing the components of the program separately and composing them later,
    showing a novel application of generative programming with program analysis.
  \end{enumerate}
\item We empirically evaluate the performance improvement by staging on
    control-flow analysis (Section~\ref{evaluation}). We compare the both
    context-insensitive and store-widening analysis.
\end{itemize}

>>>>

\paragraph{Contributions} Briefly, the contribution of the paper is twofold:
\begin{enumerate}[leftmargin=2em]
  \item Intellectually, through multi-stage programming, we present a unified construction 
    that naturally extends the first Futamura projection to abstract interpreters.
 \item Pragmatically, by case studies and empirical evaluation, we show that staging 
   abstract interpreters is useful to improve performance while untouching
   the soundness. 
\end{enumerate}
\paragraph{Organization} The paper is organized as follows:
\begin{itemize}[leftmargin=2em]
\item Starting from a generic interface of the interpreter for a small higher-order language
  (Section~\ref{prelim}), we first show the instantiation of concrete
  interpretation (Section~\ref{unstaged_conc}), and then lift it to the staged
  version by replacing the binding-time types (Section~\ref{stagedinterp}).
\item We discuss the unstaged abstract interpreter under the same framework by
  replacing the environment, store and values (Section~\ref{unstaged_abs}).
  Finally, we show the combination of approximation and specialization, dubbed
  \textit{staged abstract interpreters}, can be readily derived (Section~\ref{sai}).
\item We conduct three case studies on the applicability of our approach
  (Section~\ref{cases_study}).
  \begin{enumerate}
  \item We first revisit the Abstract Compilation (AC)
    \cite{Boucher:1996:ACN:647473.727587} (Section~\ref{cs_ac}), showing that we can
    achieve the same optimization with much less engineering effort.
  \item We extend the staged abstract interpreter to various control-flow
    analysis (Section \ref{cfa}), including context-sensitivity, store-widening, and abstract
    garbage collection, showing that our approach is widely applicable.
  \item We apply our approach to modular analysis (Section \ref{modular}),
    i.e., analyzing the components of the program separately and composing them later,
    showing a novel application of generative programming with program analysis.
  \end{enumerate}
\item We empirically evaluate the performance improvement by staging on
    control-flow analysis (Section~\ref{evaluation}). We compare the both
    context-insensitive and store-widening analysis.
\end{itemize}
